---
title: "Untitled"
author: "ryotoitoi"
date: '2022-05-14'
output: html_document
---

# Library

```{r}
library(tidyverse)
library(purrr)
library(data.table)
library(scales)
library(patchwork)
library(lemon)
library(lubridate)
library(magick)

#Choose your favorite color
mycol = c("turquoise", "lightslateblue","lightskyblue", 
          "chartreuse2", "palegreen2", "mistyrose2", "grey60", "hotpink1")
```

# Data Files

-   There seems to be "stock_list" file on the level above the training data.
-   "stock_file" probably contains information on stocks in the Tokyo market.

```{r}
data_path = "../"
train_path = paste0(data_path, "train_files/")
cat("list of the top directory\n")
list.files(data_path, full.names = T)

cat("training data\n")
list.files(train_path, full.names = T)
```

```{r}
stock_list <- fread(
  paste0(data_path, "stock_list.csv"),na.strings = c("","NULL")
  )
stock_list %>% head()
stock_list %>% tail()

cat(paste0(train_path, "stock_prices.csv"))
stock_price <- fread(
  paste0(train_path, "stock_prices.csv"), na.strings = c("", "NULL")
)
stock_price %>% head()

financials <- fread(
  paste0(train_path, "financials.csv"), na.strings = c("", "NULL")
)
financials %>% head()
```

# stock_list

**This is assumed to be information on all issues in the Tokyo market.**

I should check the columns name.

```{r}
stock_list %>% names()
stock_list %>% str()
```

```{r}
st1 <- names(stock_list)[str_detect(names(stock_list), "^[0-9]")] # detect col names which start with figure
print(st1)
st2 <- c("SectorCode_33", "SectorName_33", "SectorCode_17", "SectorName_17")
setnames(stock_list, st1, st2) # replace col name st1 to st2


st1 <- names(stock_list)[str_detect(names(stock_list), "/")] %>% 
  str_replace_all("/", "_")

setnames(stock_list, names(stock_list)[str_detect(names(stock_list), "/")], st1)

glimpse(stock_list)
```

```{r}
?glimpse
```

## Generate the list of unique_values

```{r}
sapply(stock_list, function(x){length(unique(x))}) %>% 
  data.table(colname = names(.), unique_values = .)
```

**A brief comparsion of old and new market segments.**

```{r}
stock_list[, n:= 1:.N, by= Section_Products]
stock_list
stock_list[n ==1] %>% 
  select(Section_Products, NewMarketSegment) 
```

-   The new segments(4/4/2022\~) seems simpler and easier to understand.

# Stock Price

```{r}
glimpse(stock_price)
```

-   This appears to be a pure record of price movement.
-   What is "target" ??

**How many stocks should we forecast?**

```{r}
stock_price %>% 
  select(SecuritiesCode) %>% 
  unique() %>% 
  nrow()
```

-   The forecast covers 2,000 stocks out of 4,417 stocks.

## Date period

```{r}
stock_price %>% 
  mutate(., Date = as.IDate(Date))

range(stock_price$Date)
```

-   All data are from the market classification (Section_Products).

# financials

```{r}
glimpse(financials)
```

**Convert some strings into numerical.** **Corrects time data to iTime**

```{r}
cols <- names(financials)[c(13:36, 43:45)]
financials[, (cols) := lapply(.SD, as.numeric), .SDcols = cols] # .SD is "Self-reference of the Data"
financials$DisclosedTime <- as.ITime(financials$DisclosedTime)
```

```{r}
glimpse(financials)
```

# Check for unique value and NA.

```{r}
df_tmp <- financials %>% 
  sapply(function(x){length(unique(x))}) %>% 
  data.table(feature = names(.), unique_values = .)

df_tmp2 <- colSums(sapply(financials, is.na)) %>% 
  data.table(feature = names(.), NAs = .)

df_tmp
df_tmp2

cat("nrow = ", nrow(financials))

df_tmp <- df_tmp %>% 
  left_join(df_tmp2, by = "feature") %>% 
  mutate(ColNo = row_number())
df_tmp
view(df_tmp)
```

**The following may be paticularly relevant to stock price movements in this context.**

1.  EaringsPerShare:一株当たり利益
2.  ForecastEarningsPerShare:予測一株当たり利益
3.  DisclosedDate:開示日

-   If the expected earings per share is higher than the previous period, the stock price may rise in the future. Unfortunately, there seems to be a lot of NA.
-   Price movements are expected to be large on the disclosure date.

**The stock market closes at 3:00 p.m.**
We believe that earnings disclosure after 3:00 p.m. has a greater impact on price movements the next day than  on that day.
For this reason, I will move the disclosure date by one day for earnings discoosures after 3:00 p.m.

```{r}
financials %>% 
  mutate(
    DisclosedDate = if_else(
      DisclosedTime>=as.ITime("15:00:00"), DisclosedDate + 1, DisclosedDate
      )
    )
```

**rename columns**
```{r}
financials %>% 
  setnames(names(financials)[43], "NumberOfIssued")
financials %>% names()
```

**Consider missing value completion for ForecastEarningsPerShare.**
I believe earnings per share can be obtained by dividing earnings by the number of shares outstanding.

```{r}
financials <- financials %>% 
  mutate(ForecastEarningsPerShare2 = round(ForecastProfit / NumberOfIssued ,  digits = 1))

financials %>% 
  names()
```

**Check to see if the value is available.**
```{r}
financials %>% 
  select(ForecastEarningsPerShare, ForecastEarningsPerShare2) %>% 
  head(20)
```
```{r}
financials %>% 
  filter(!is.na(ForecastEarningsPerShare2) & is.na(ForecastEarningsPerShare)) %>% 
  nrow()
```

- 846 cases could be completed. It is not so much, but I will interpolate.

```{r}
financials <- financials %>%
  mutate(
    ForecastEarningsPerShare = if_else(is.na(ForecastEarningsPerShare),
                                       ForecastEarningsPerShare2,
                                       ForecastEarningsPerShare)
  )

financials %>% 
  filter(!is.na(ForecastEarningsPerShare2) & is.na(ForecastEarningsPerShare)) %>% 
  nrow()
```

**Create Disclosed(1 or 0) when I combine them later.**
```{r}
financials <- financials %>% 
  mutate(disclosed = 1)
financials %>% select(disclosed)
```


# Combining Data Sets
Let's combine the stock price data set with stock information and financial performance information.

```{r}
stock_list

df_comb <- stock_price %>% 
  left_join(stock_list %>% select(1,3:9), by = "SecuritiesCode") # conbine stock_price with stock_list
```

```{r}
df_comb <- df_comb %>% 
  left_join(
  financials %>% select(DisclosedDate, SecuritiesCode, EarningsPerShare, ForecastEarningsPerShare, disclosed) %>% rename(Date = DisclosedDate), 
  by = c("Date", "SecuritiesCode")
  )

df_comb

df_comb <- df_comb %>% 
  mutate(
    disclosed = if_else(
    is.na(disclosed), 
    0,
    disclosed
    )
  )

df_comb %>% head(10)
```


```{r}
df_stock_list_count <- stock_list %>% 
  count(NewMarketSegment) %>% 
  arrange(desc(n)) %>% 
  rename(stock_list = n)

df_stock_list_count

df_stock_price_count <- df_comb %>% 
  group_by(NewMarketSegment, SecuritiesCode) %>% 
  count() %>% 
  group_by(NewMarketSegment) %>% 
  count() %>% 
  rename(stock_price = n)

df_stock_price_count

df_tmp <- left_join(df_stock_list_count, df_stock_price_count, by = "NewMarketSegment")
df_tmp %>%
  mutate(rate = round(stock_price/stock_list, digits = 2))
```
- It appears that about 90% of the current prime market and 20% of remaining market issues are covered.

```{r}

```




















