---
title: "Untitled"
author: "ryotoitoi"
date: '2022-05-14'
output: html_document
---

# Library

```{r}
library(tidyverse)
library(purrr)
library(data.table)
library(scales)
library(patchwork)
library(lemon)
library(lubridate)
library(magick)

#ggplot setting
theme_set(theme_minimal() +
         theme(plot.title = element_text(size = 9, face = "bold"),
               plot.subtitle = element_text(size  = 9, face = "bold"),
               axis.text.x = element_text(size = 9),
               axis.text.y = element_text(size = 9),
               axis.title.x = element_text(size = 9),
               axis.title.y = element_text(size = 9),
               legend.text = element_text(size = 9),
               legend.title = element_text(size = 9),
               strip.text.x = element_text(size = 9)
              )
          )

#Choose your favorite color
mycol = c("turquoise", "lightslateblue","lightskyblue", 
          "chartreuse2", "palegreen2", "mistyrose2", "grey60", "hotpink1")
```


# Data Files

-   There seems to be "stock_list" file on the level above the training data.
-   "stock_file" probably contains information on stocks in the Tokyo market.

```{r}
data_path = "../"
train_path = paste0(data_path, "train_files/")
cat("list of the top directory\n")
list.files(data_path, full.names = T)

cat("training data\n")
list.files(train_path, full.names = T)
```

```{r}
stock_list <- fread(
  paste0(data_path, "stock_list.csv"),na.strings = c("","NULL")
  )
stock_list %>% head()
stock_list %>% tail()

cat(paste0(train_path, "stock_prices.csv"))
stock_price <- fread(
  paste0(train_path, "stock_prices.csv"), na.strings = c("", "NULL")
)
stock_price %>% head()

financials <- fread(
  paste0(train_path, "financials.csv"), na.strings = c("", "NULL")
)
financials %>% head()
```

# stock_list

**This is assumed to be information on all issues in the Tokyo market.**

I should check the columns name.

```{r}
stock_list %>% names()
stock_list %>% str()
```

```{r}
st1 <- names(stock_list)[str_detect(names(stock_list), "^[0-9]")] # detect col names which start with figure
print(st1)
st2 <- c("SectorCode_33", "SectorName_33", "SectorCode_17", "SectorName_17")
setnames(stock_list, st1, st2) # replace col name st1 to st2


st1 <- names(stock_list)[str_detect(names(stock_list), "/")] %>% 
  str_replace_all("/", "_")

setnames(stock_list, names(stock_list)[str_detect(names(stock_list), "/")], st1)

glimpse(stock_list)
```

```{r}
?glimpse
```

## Generate the list of unique_values

```{r}
sapply(stock_list, function(x){length(unique(x))}) %>% 
  data.table(colname = names(.), unique_values = .)
```

**A brief comparsion of old and new market segments.**

```{r}
stock_list[, n:= 1:.N, by= Section_Products]
stock_list
stock_list[n ==1] %>% 
  select(Section_Products, NewMarketSegment) 
```

-   The new segments(4/4/2022\~) seems simpler and easier to understand.

# Stock Price

```{r}
glimpse(stock_price)
```

-   This appears to be a pure record of price movement.
-   What is "target" ??

**How many stocks should we forecast?**

```{r}
stock_price %>% 
  select(SecuritiesCode) %>% 
  unique() %>% 
  nrow()
```

-   The forecast covers 2,000 stocks out of 4,417 stocks.

## Date period

```{r}
stock_price %>% 
  mutate(., Date = as.IDate(Date))

range(stock_price$Date)
```

-   All data are from the market classification (Section_Products).

# financials

```{r}
glimpse(financials)
```

**Convert some strings into numerical.** **Corrects time data to iTime**

```{r}
cols <- names(financials)[c(13:36, 43:45)]
financials[, (cols) := lapply(.SD, as.numeric), .SDcols = cols] # .SD is "Self-reference of the Data"
financials$DisclosedTime <- as.ITime(financials$DisclosedTime)
```

```{r}
glimpse(financials)
```

# Check for unique value and NA.

```{r}
df_tmp <- financials %>% 
  sapply(function(x){length(unique(x))}) %>% 
  data.table(feature = names(.), unique_values = .)

df_tmp2 <- colSums(sapply(financials, is.na)) %>% 
  data.table(feature = names(.), NAs = .)

df_tmp
df_tmp2

cat("nrow = ", nrow(financials))

df_tmp <- df_tmp %>% 
  left_join(df_tmp2, by = "feature") %>% 
  mutate(ColNo = row_number())
df_tmp
view(df_tmp)
```

**The following may be paticularly relevant to stock price movements in this context.**

1.  EaringsPerShare:一株当たり利益
2.  ForecastEarningsPerShare:予測一株当たり利益
3.  DisclosedDate:開示日

-   If the expected earings per share is higher than the previous period, the stock price may rise in the future. Unfortunately, there seems to be a lot of NA.
-   Price movements are expected to be large on the disclosure date.

**The stock market closes at 3:00 p.m.**
We believe that earnings disclosure after 3:00 p.m. has a greater impact on price movements the next day than  on that day.
For this reason, I will move the disclosure date by one day for earnings discoosures after 3:00 p.m.

```{r}
financials <- financials %>% 
  mutate(
    DisclosedDate = if_else(
      DisclosedTime>=as.ITime("15:00:00"), 
      DisclosedDate + 1, DisclosedDate
      )
    )
```


**rename columns**
```{r}
financials %>% 
  setnames(names(financials)[43], "NumberOfIssued")
financials %>% names()
```


**Consider missing value completion for ForecastEarningsPerShare.**
I believe earnings per share can be obtained by dividing earnings by the number of shares outstanding.

```{r}
financials <- financials %>% 
  mutate(ForecastEarningsPerShare2 = round(ForecastProfit / NumberOfIssued ,  digits = 1))

financials %>% 
  names()
```

**Check to see if the value is available.**
```{r}
financials %>% 
  select(ForecastEarningsPerShare, ForecastEarningsPerShare2) %>% 
  head(20)
```
```{r}
financials %>% 
  filter(!is.na(ForecastEarningsPerShare2) & is.na(ForecastEarningsPerShare)) %>% 
  nrow()
```

- 846 cases could be completed. It is not so much, but I will interpolate.

```{r}
financials <- financials %>%
  mutate(
    ForecastEarningsPerShare = if_else(is.na(ForecastEarningsPerShare),
                                       ForecastEarningsPerShare2,
                                       ForecastEarningsPerShare)
  )

financials %>% 
  filter(!is.na(ForecastEarningsPerShare2) & is.na(ForecastEarningsPerShare)) %>% 
  nrow()
```

**Create Disclosed(1 or 0) when I combine them later.**
```{r}
financials[, disclosed := 1]
financials %>% select(disclosed)
```


# Combining Data Sets
Let's combine the stock price data set with stock information and financial performance information.

```{r}
stock_list

df_comb <- stock_price %>% 
  left_join(stock_list %>% select(1,3:9), by = "SecuritiesCode") # combine stock_price with stock_list
```

```{r}
df_comb <- df_comb %>% 
  left_join(
  financials %>% select(DisclosedDate, SecuritiesCode, EarningsPerShare, ForecastEarningsPerShare, disclosed) %>% rename(Date = DisclosedDate), 
  by = c("Date", "SecuritiesCode")
  )

df_comb

df_comb[is.na(disclosed), disclosed := 0]

df_comb %>% head(10)
```


```{r}
df_stock_list_count <- stock_list %>% 
  count(NewMarketSegment) %>% 
  arrange(desc(n)) %>% 
  rename(stock_list = n)

df_stock_list_count

df_stock_price_count <- df_comb %>% 
  group_by(NewMarketSegment, SecuritiesCode) %>% 
  count() %>% 
  group_by(NewMarketSegment) %>% 
  count() %>% 
  rename(stock_price = n)

df_stock_price_count

df_tmp <- left_join(df_stock_list_count, df_stock_price_count, by = "NewMarketSegment")
df_tmp %>%
  mutate(rate = round(stock_price/stock_list, digits = 2))
```
- It appears that about 90% of the current prime market and 20% of remaining market issues are covered.

```{r}
options(repr.plot.width = 15, repr.plot.height = 8)

df_stock_list_sector <- stock_list %>% 
  group_by(SectorName_33, SecuritiesCode) %>% 
  summarise(n = n()) %>% 
  group_by(SectorName_33) %>% 
  summarise(n = n()) %>% 
  arrange(desc(n)) %>% 
  ungroup()

df_stock_list_sector

g1 <- df_stock_list_sector %>% 
  ggplot()+
  geom_bar(
    aes(x = reorder(SectorName_33, n), y = n), 
    stat = "identity", 
    fill = mycol[2], 
    alpha = 0.5)+
  coord_flip()+
  labs(title = "Sector of the forecasted stocks", x = "")

show(g1)

df_stock_price_sector <- df_comb %>% 
  group_by(SectorName_33, SecuritiesCode) %>% 
  count() %>% 
  group_by(SectorName_33) %>% 
  count()

g2 <- df_stock_price_sector %>% 
  ggplot()+
  geom_bar(
    aes(x = reorder(SectorName_33, n), y = n),
    stat = "identity",
    fill = mycol[1],
    alpha = 0.5
 ) + 
  coord_flip()+
  labs(title = "Sector of the Tokyo Market stocks", x = "")

g2
```

```{r}
g1 / g2
```

- About half of the stocks in each sector appear to be set as forecast stocks. The "_" in the graph on the right is considered an index issue.

```{r}
range(df_comb$Date)
```


```{r}
sector_name_code_33 <- df_comb %>% 
  group_by(SectorCode_33, SectorName_33) %>% 
  count()

sector_name_code_33 %>% 
  arrange(desc(n))

sector_name_code_17 <- df_comb %>% 
  group_by(SectorCode_17, SectorName_17) %>% 
  count()

sector_name_code_17 %>% 
  arrange(desc(n))
```

# Stock charts

**Visialization is performed with a set of three charts.**
- The upper chart shows the forecast earnings per share for current period, the middle chart shows the stock price, and the lower chart shows the Target.
- The pink vertical line indicates the date of earnings disclosure.

```{r}
cat(as.POSIXct("2023-12-02"))
```


```{r}
make_stock_chart <- function(code){
    
    df_tmp <- df_comb[SecuritiesCode == code]
    disclosed_date <- as.POSIXct(df_tmp[disclosed == 1, Date])
    
    x_min <- "2017-02-01"
    x_max <- "2021-11-30"
    x_range <- c(as.POSIXct(x_min), as.POSIXct(x_max))
    
    TL <- paste0(df_tmp$SecuritiesCode[1], ":", 
                 df_tmp$Name[1], ":", 
                 df_tmp$NewMarketSegment[1])
    
    g1 <- 
      df_tmp[!is.na(ForecastEarningsPerShare)] %>% 
      mutate(DATE = as.POSIXct(Date)) %>%
      ggplot(aes(x = DATE, y = ForecastEarningsPerShare))+
      geom_point(alpha = 0.7)+
      geom_line(color = "darkgray", alpha = 0.8)+
      geom_vline(xintercept = disclosed_date, color = mycol[8], alpha = 0.5)+
      scale_x_datetime(breaks = "2 months", date_labels = "%Y-%m", limits = x_range)+
      theme(axis.text.x = element_text(angle = 90, hjust = 1))+
      labs(titles = TL, x = "")
    
    g2 <-
      df_tmp[!is.na(Close)] %>% mutate(DATE = as.POSIXct(Date)) %>%
      ggplot(aes(x = DATE, y = Close))+
      geom_line(alpha = 0.7)+
      geom_vline(xintercept = disclosed_date, linetype = "dashed",color = mycol[8], alpha = 0.7)+
      scale_x_datetime(breaks = "2 months", date_labels = "%Y-%m", limits = x_range)+
      theme(axis.text.x = element_text(angle = 90, hjust = 1))+
      labs(titles = TL, x = "")
    
    g3<-
      df_tmp[SecuritiesCode == code][!is.na(Close)] %>% 
      mutate(DATE = as.POSIXct(Date)) %>%
      ggplot(aes(x = DATE, y = Target))+
      geom_line(alpha = 0.7)+
      geom_vline(xintercept = disclosed_date, color = mycol[8], alpha = 0.5)+
      scale_x_datetime(breaks = "2 months", date_labels = "%Y-%m", limits = x_range)+
      scale_y_continuous(breaks = seq(-0.2, 0.2, 0.04), limits = c(-0.16, 0.16))+
      theme(axis.text.x = element_text(angle = 90, hjust = 1))+
      labs(titles = TL, x = "")
    
    return (g1/g2/g3 + plot_layout(height = c(2, 2, 4)))
    
}
```

```{r}
make_stock_chart(2153)
```

```{r}

df_tmp <- df_comb %>% 
  filter(SecuritiesCode == 2153)

disclosed_date <- as.POSIXct(df_tmp[disclosed == 1, Date])
print(disclosed_date)

x_min <- "2017-02-01"
x_max <- "2021-11-30"
x_range <- c(as.POSIXct(x_min), as.POSIXct(x_max))

cat(x_range)

TL <- paste0(df_tmp$SecuritiesCode[1], ":", 
             df_tmp$Name[1], ":", 
             df_tmp$NewMarketSegment[1])

print(TL)

g1 <- 
  df_tmp[!is.na(ForecastEarningsPerShare)] %>% 
  mutate(DATE = as.POSIXct(Date)) %>%
  ggplot(aes(x = DATE, y = ForecastEarningsPerShare))+
  geom_point(alpha = 0.7) + 
  geom_line(color = "darkgray", alpha = 0.8) +
  geom_vline(xintercept = disclosed_date, color = mycol[8], alpha = 0.5) + 
  scale_x_datetime(breaks = "2 months", date_labels = "%Y-%m", limits = x_range) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(titles = TL, x = "")

g2 <- 
    df_tmp[!is.na(Close)] %>% mutate(DATE = as.POSIXct(Date)) %>%
    ggplot(aes(x = DATE, y = Close))+
    geom_line(alpha = 0.7)+
    geom_vline(xintercept = disclosed_date, linetype = "dashed",color = mycol[8], alpha = 0.7)+
    scale_x_datetime(breaks = "2 months", date_labels = "%Y-%m", limits = x_range)+
    theme(axis.text.x = element_text(angle = 90, hjust = 1))+
    labs(titles = TL, x = "")

show(g1 / g2)
```
















